\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-06-01 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

>>>>

%%  LocalWords:  checkboard % Copyright 2007, 2008, 2009 Elsevier Ltd
%
% This file is part of the 'Elsarticle Bundle'.
% ---------------------------------------------
%
% It may be distributed under the conditions of the LaTeX Project Public
% License, either version 1.2 of this license or (at your option) any
% later version.  The latest version of this license is in
%    http://www.latex-project.org/lppl.txt
% and version 1.2 or later is part of all distributions of LaTeX
% version 1999/12/01 or later c.
%
% The list of all files belonging to the 'Elsarticle Bundle' is
% given in the file `manifest.txt'.
%

\title{ \blue{Numerical investigation of viscous flow instabilities through heterogeneous porous media using adaptive and unstructured meshes under different mobility scenarios - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\section{Introduction}\label{section:intro}
\medskip
Numerical investigation of multiphase flows in porous media have attracted the attention of the scientific community over the past 40 years. Characterisation of fluid flow through porous media serves as the foundation of reservoir engineering and groundwater studies. %Oil and gas migration in reservoirs and transport of contaminants in groundwater are some of important physical problems in which porous media flows play a crucial role. 
%Reservoir engineers and hydro-geologists are dealing with complex geometries, irregular boundaries and heterogeneous geological formations.
Underground coal gasification is another important area of interest and, more recently due to global environmental problems several research work have focused on CO$_{\text{2}}$ migration and trapping mechanisms in carbon capture utilisation and storage (CCUS) operations~\citep{spycher_2003, chen_2006, self_2012, pruess_1990c, white_1981,jiang_2011}.

\medskip
Due to complex and/or heterogeneous geological formations, detailed modelling and simulation of multiphase flows through porous media is crucial to understand the aforementioned processes. Description of physics and mechanisms of multiphase flows were reported by \citet{wooding_1976} with focus on capillary pressure and the flow regimes in capillary media. A comprehensive review of mechanisms of fingering (i.e., fluid instability) and forces acting on the interface between two immiscible fluids can be found in \citet{homsy_1987}. \citet{adler_1988} described both microscopic and macroscopic scale darcy-equations.
% Nevertheless we should refer to the area of flow instabilities  as these, first described by \citet{saffman_1958} \red{(IS THIS TRUE? SAFFMANN MAY HAVE BEEN THE FIRST TO THROUGHLY DISCUSS VISCOUS INSTABILITIES, BUT THERE WERE OTHER SCIENTISTS THAT DESCRIBED FLUID INSTABILITIES BEFORE, E.G., RAYLEIGH(1896), TAYLOR (1955) ETC)}. 
The first distinction should be made between microscopic and macroscopic instabilities. Microscopic instabilities describe phenomena occurring locally, for example, Kelvin-Helmholtz and Saffman-Taylor instabilities \citep{saffman_1959}. On the other hand, macroscopic instabilities involve two-phase flow system \citep{bottoni_1992}. This paper will focus on microscopic instabilities and phenomena in two-phase systems that mainly occur due to viscous and stress forces and often referred as viscous instabilities or \textit{viscous fingering}.

\medskip
Figure \ref{fig:3testcase_a} illustrates another set of simulations for when another region (inlet) of fluid $1$ ins introduced into the formation. This time fluid $1$ is injected from both the left hand side and the upper left corner of the domain, at a velocity u=$0.5$ while the set up of the problem remains the same, the mobility ratio is $10$, and the adaptive and ustructured mesh is implied. The top layer is saturated with phase $2$, while the rest of the domain has a saturation of $0.1$. The major difference is located in the velocity fields %(see Fig.\ref{fig:vel_magn2}) 
as the presence of this extra inlet increases the flow at the top layers. At this point is proper to mentioned the extreme case, see Fig.\ref{fig:4testcase}, when mobility ratio is even an order of magnitude higher, when MR=$100$, 
%this case is unlikely to happen as the mobility ration of the existing fluids in the industry , 
it is a test-case that can illustrate the higher, faster and more profound development of instabilities. Also by focusing the grid resolution in the saturation front, \citet{christou_2015}  demonstrated the explicit formation of fingers formed due to the instability in the pressure ﬁeld and triggered by viscosity ratio. A comparison has also been made by using a low resolution element, the $P_{1}DG-P_{1}DG$. No fingers could be observed due to mesh coarseness (fingers were observed in ﬁner uniform and adaptive meshes). The last case that will give an estimable and quantitative description to the reader is the when the mobility ration is highly increased into $100$. Screenshots of the phase volume fraction and the development of fingers will are shown in fig.\ref{fig:4testcase_a}.

%% References with bibTeX database:
\bibliographystyle{elsarticle-harv} 
\bibliography{references}
\clearpage

\listoftables
\clearpage

\input{article_table}
\clearpage

\listoffigures
\clearpage
